miniKanren with fair search strategies

### 2019-05-05 Paper/paper.tex
bullet points

To summarize our contribution, we
\begin{itemize}
	\item analyze an existing concept, fair \disj{} by 
	\citet{seres1999algebra}.
	\item propose a new concept, almost-fair \disj{}.
	\item propose a new definition of fair \disj{}.
	\item propose and implement balanced interleaving depth-first search 
	(DFS$_\textrm{bi}$), a new search strategy with almost-fair \disj{}.
	\item propose and implement fair depth-first search (DFS$_\textrm{f}$), a 
	new search strategy with fair \disj{}.
	\item implement in a new way breath-first search (BFS), a search strategy 
	with fair \disj{} and fair \conj{}.
	(our code runs faster in all benchmarks and is simpler)
	\item prove our BFS implementation is equivalent with the one by 
	\citet{seres1999algebra}.
\end{itemize}

>>>>

To summarize our contribution, we
\begin{itemize}
	\item propose and implement balanced interleaving depth-first search 
	(DFS$_\textrm{bi}$), a new search strategy with almost-fair \disj{}.
	\item propose and implement fair depth-first search (DFS$_\textrm{f}$), a 
	new search strategy with fair \disj{}.
	\item implement in a new way breath-first search (BFS), a search strategy 
	with fair \disj{} and fair \conj{}. (our code runs faster in all 
benchmarks and is simpler). And we prove formally that our BFS implementation 
is equivalent to the one by \citet{seres1999algebra}.
\end{itemize}
